Approximation as Differentiation: Notes

### 2025-07-04 notes/predicate-system.tex
Ok need to fix the predicate system over Set.

Suppose $\mathcal{S} = (\Pred, \top, \meet, \join, \residual, \forall)$ a predicate system over $\Set$,
$\cat{C}$ a category and $F: \cat{C}^\op \to \Set$ a presheaf. Define a predicate on $F$ to be a family of
predicates $P_X \in \Pred(F(X))$ for every object $X$ in $\cat{C}$ such that $P_Y \sqsubseteq
\reindex{P_X}{F(f)}$ for every $f: X \to Y$ in $\cat{C}$.

>>>>

Suppose $\mathcal{S} = (\Pred, \top, \meet, \join, \residual, \forall)$ a predicate system over $\Set$,
$\cat{C}$ a category and $F: \cat{C}^\op \to \Set$ a presheaf. Define a \emph{predicate on $F$} to be a family
of predicates $P_X \in \Pred_\mathcal{S}(F(X))$ for every object $X$ in $\cat{C}$ such that $P_Y \sqsubseteq
\reindex{P_X}{F(f)}$ for every $f: X \to Y$ in $\cat{C}$.

Now define the predicate system $\mathcal{S}^{\cat{C}}$ over $\Func{\cat{C}^\op}{\Set}$ which assigns to every
presheaf $F$ the poset $(\Pred(F), \sqleq)$ of predicates on $F$ ordered pointwise, and where $\top, \meet,
\join, \residual$ and $\forall$ in $\Pred(F)$ are all given pointwise. For every natural transformation
$\alpha: F \to G$, the pullback $\reindex{-}{\alpha}: \Pred(G) \to \Pred(F)$ ...
